Kernel k-Groups via Hartigan's Method

### 2019-09-26 energy_clustering/pami18/energy_clustering.tex
does this work?

\author{Guilherme~Fran\c ca,~Maria L.~Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. T. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering and Institute for Computational
Medicine, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. L. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}}

@@

\begin{figure*}
\centering
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{gauss_1d.pdf}\\[-2em](a)
\end{minipage}
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{loggauss_1d.pdf} \\[-2em](b)
\end{minipage}\\[1em]
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{normal_density2.pdf}\\[-2em](c)
\end{minipage}\hspace{2em}
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{lognormal_density2.pdf}\\[-2em](d)
\end{minipage}
\caption{
\label{fig:1dexperiment}
Clustering one-dimensional data for a two-class problem.
(a) Data normally distributed as
$x \stackrel{iid}{\sim} (1/2) \mathcal{N}(0, 1.5) +
(1/2) \mathcal{N}(1.5,0.3)$. (b) Data following lognormal distributions
as $x \stackrel{iid}{\sim}
(1/2)e^{\mathcal{N}(0, 1.5)} + (1/2) e^{\mathcal{N}(1.5, 0.3)}$.
In both cases we plot the average accuracy versus the total number of points
(error bars are too small to be visible).
(c) For the same distribution as in item (a), we sample 2000
points, cluster them with the three methods, then perform a kernel density 
estimation for kernel k-groups, since this is a model-free method,
while for k-means and GMM we show the estimated Gaussian for each
class.
The clustering accuracy for each method is in Table~\ref{tb:dens}.
(d) Exactly the same experiment but for the distribution in item (b). 
Note that only kernel k-groups is able to distinguish between the two classes
in this example.
}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.19\textwidth]{gauss_means_scatter.pdf}
\includegraphics[width=0.19\textwidth]{gauss_cov_scatter.pdf}
\includegraphics[width=0.19\textwidth]{gauss_diff_metrics.pdf}
\includegraphics[width=0.19\textwidth]{loggauss_diff_metrics.pdf}
\includegraphics[width=0.19\textwidth]{unbalanced_scatter.pdf}
\put(-500,-8){(a)}
\put(-398,-8){(b)}
\put(-298,-8){(c)}
\put(-195,-8){(d)}
\put(-95,-8){(e)}
\caption{
\label{fig:scatter}
Scatter plot of the last two dimensions where $\mu_2$ has signal.
Each plot has 200 points total.
(a) Data distributed as in \eqref{eq:gauss1}.
(b) Data distributed as in \eqref{eq:gauss2}.
(c) Data distributed as in \eqref{eq:20gauss}.
(d) Parameters as in \eqref{eq:20gauss} but for lognormal mixture.
(e) Data from \eqref{eq:gauss3} with $N = 300$ and $m=200$.
}
\end{figure*}

>>>>

\author{Guilherme~Fran\c ca,~Maria L.~Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. T. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering, Institute for Computational
Medicine, and Kavli Neuroscience Discovery Institute, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. L. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}}

@@

\begin{figure*}
\centering
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{gauss_1d.pdf}\\[-2em](a)
\end{minipage}
\begin{minipage}{.4\textwidth}
\includegraphics[width=1\textwidth]{loggauss_1d.pdf} \\[-2em](b)
\end{minipage}\\[1em]
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{normal_density2.pdf}\\[-2em](c)
\end{minipage}\hspace{2em}
\begin{minipage}{.37\textwidth}
\includegraphics[width=1\textwidth]{lognormal_density2.pdf}\\[-2em](d)
\end{minipage}
\caption{
\label{fig:1dexperiment}
Clustering one-dimensional data for a two-class problem.
(a) Data normally distributed as
$x \stackrel{iid}{\sim} (1/2) \mathcal{N}(0, 1.5) +
(1/2) \mathcal{N}(1.5,0.3)$. (b) Data following lognormal distributions
as $x \stackrel{iid}{\sim}
(1/2)e^{\mathcal{N}(0, 1.5)} + (1/2) e^{\mathcal{N}(1.5, 0.3)}$.
In both cases we plot the average accuracy versus the total number of points
(error bars are too small to be visible).
(c) For the same distribution as in item (a), we sample 2000
points, cluster them with the three methods, then perform a kernel density 
estimation for kernel k-groups, since this is a model-free method,
while for k-means and GMM we show the estimated Gaussian for each
class.
The clustering accuracy for each method is in Table~\ref{tb:dens}.
(d) Exactly the same experiment but for the distribution in item (b). 
Note that only kernel k-groups is able to distinguish between the two classes
in this example.
}
% todo i don't understand what the filled in content is? is that showing the truth? gotta state it whatever it is.  i would remove the black lines labeled truth if you keep the filled.
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.19\textwidth]{gauss_means_scatter.pdf}
\includegraphics[width=0.19\textwidth]{gauss_cov_scatter.pdf}
\includegraphics[width=0.19\textwidth]{gauss_diff_metrics.pdf}
\includegraphics[width=0.19\textwidth]{loggauss_diff_metrics.pdf}
\includegraphics[width=0.19\textwidth]{unbalanced_scatter.pdf}
\put(-500,-8){(a)}
\put(-398,-8){(b)}
\put(-298,-8){(c)}
\put(-195,-8){(d)}
\put(-95,-8){(e)}
\caption{
\label{fig:scatter}
Scatter plot of the last two dimensions where $\mu_2$ has signal.
Each plot has 200 points total.
(a) Data distributed as in \eqref{eq:gauss1}.
(b) Data distributed as in \eqref{eq:gauss2}.
(c) Data distributed as in \eqref{eq:20gauss}.
(d) Parameters as in \eqref{eq:20gauss} but for lognormal mixture.
(e) Data from \eqref{eq:gauss3} with $N = 300$ and $m=200$.
% i'd make the points bigger.
}
\end{figure*}
